Non-word repetition in Yélî Dnye

### 2020-09-07 manuscript.Rmd
make table render

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

@@

```{r tab2-stims}
#add orthographic representations targets & other stims chars
stims <- read_delim("stimuli2.txt", delim = "\t")
stims=stims[order(stims[,1]),-3]
colnames(stims)<-c("Type","Orthographic","Phonological")
cbindX(stims[stims$Type=="practice",],
      stims[stims$Type==1,],
      stims[stims$Type==2,],
      stims[stims$Type==3,],
      stims[stims$Type==4,])

stims=stims[,-1]

# mytab2 = kable(stims, "latex", booktabs = T,caption="NWR stimuli in orthographic and phonological representations.", row.names =F) %>%
# kable_styling() %>%
# add_header_above(c("Practice" = 2, "Monosyll" = 2, "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))
# mytab2

>>>>

lang              : "english"
class             : "man"
output            :
  papaja::apa6_pdf:
    latex_engine: xelatex
---

@@

```{r tab2-stims, results = "asis"}
#add orthographic representations targets & other stims chars
stims <- read_delim("stimuli2.txt", delim = "\t") %>%
  arrange(factor(type, levels = c("practice", "1", "2", "3", "4"))) %>%
  select(type, target_ortho, phono) %>%
  rename("Type" = type, "Orthographic" = target_ortho, "Phonological" = phono)

# probably a nicer way to do this but anyhow...
practice.stims <- filter(stims, Type == "practice")[,2:3]
practice.stims$row <- seq(1:nrow(practice.stims))
syll1.stims <- filter(stims, Type == "1")[,2:3]
syll1.stims$row <- seq(1:nrow(syll1.stims))
syll2.stims <- filter(stims, Type == "2")[,2:3]
syll2.stims$row <- seq(1:nrow(syll2.stims))
syll3.stims <- filter(stims, Type == "3")[,2:3]
syll3.stims$row <- seq(1:nrow(syll3.stims))
syll4.stims <- filter(stims, Type == "4")[,2:3]
syll4.stims$row <- seq(1:nrow(syll4.stims))
stims.wide <- practice.stims %>%
  full_join(syll1.stims, by = "row") %>%
  full_join(syll2.stims, by = "row") %>%
  full_join(syll3.stims, by = "row") %>%
  full_join(syll4.stims, by = "row") %>%
  select(-row) %>%
  replace(is.na(.), "")
colnames(stims.wide) <- c(
  "Orth.", "Phon.",
  "Orth.", "Phon.",
  "Orth.", "Phon.",
  "Orth.", "Phon.",
  "Orth.", "Phon."
)

kable(stims.wide,
  "latex", booktabs = T,
  caption="NWR stimuli in orthographic and phonological representations.",
  row.names =F) %>%
  kable_styling() %>%
  add_header_above(c("Practice" = 2, "Monosyll" = 2,
    "Bisyll" = 2, "Trisyll" = 2, "Tetrasyll" = 2))
